Market Simulator

### 2020-08-17 analysis/05_market_simulator.Rmd
working on persona matrix multiplication

# # Beta's we want for the plotly
# public_political_social_charity_demo <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')) %>% 
#   group_by(i) %>% 
#   summarize(theta_mean = mean(Theta))
# 
# # RenderPlotly code for testing
# 
# renderPlotly({
#   choice <- df()
  # ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  # gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  # 
  # data <- c(ai_exp_util, gp_exp_util)
  # df <- as.data.frame(matrix(data, 8, 1))
  # 
  # df[,2] <- c("Amnesty International", "Green Peace")
  # df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
  # colnames(df) <- c("Value", "Organization", "Type")

# test <- as.data.frame(matrix(runif(10), 8, 1))
# 
# test[,2] <- c("Amnesty International", "Green Peace", "Oxfam", "Red Cross")
# test[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
# colnames(test) <- c("Value", "Organization", "Type")
# 
# colors <- c("#ffc30b", "#3fad48", "#006633", "#660000")
# 
#   ggplotly(
#     ggplot(test, aes(y = Value, x = Organization, fill = Organization)) +
#            geom_col() +
#            labs(x="") +
#            scale_fill_manual(values = colors) +
#            theme(legend.position = "none") +
#            facet_wrap(~Type)
#   )
# })

@@

renderPlotly({
  choice = df()

    persona1 = p_beta1 # add step to matrix multiply the persona reactive element to the persona data and the public_political beta table.

  ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
  gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
  ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
  rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)

@@

    persona2 = p_beta2 # Choose the persona

  ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
  gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
  ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
  rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)

@@

      persona3 = p_beta3 # Choose the persona

  ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
  gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
  ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
  rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)

@@

```{r plot ai plot}
renderPlotly({
  choice = df()

    persona1 = p_beta1 # Choose the persona

  ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
  gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
  ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
  rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)

    persona2 = p_beta2 # Choose the persona

  ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
  gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
  ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
  rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)

      persona3 = p_beta3 # Choose the persona

  ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
  gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
  ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
  rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)

  data <- c(ai_exp_util1, ai_rate1, 
            ai_exp_util2, ai_rate2,
            ai_exp_util3, ai_rate3)

  df <- as.data.frame(matrix(data, 6, 1))

  df[,2] <- c("Amnesty International")
  df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
  df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
  colnames(df) <- c('Value', 'Organization', "Type", "Persona")

  ggplotly(df %>% filter(Type == "Market Share") %>% 
             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
             geom_bar(position = "dodge", stat = "identity") +
             labs(x="") + 
             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
             theme(legend.position = "none")
    )
})
```

@@

# Some kind of Org Id that could select the organization you are looking at? Not sure how to make it change the label in the graph
selectInput("org_id",
            label = "Select Organization:",
            choices = c("Amnesity International",
                        "Green Peace",
                        "Oxfam",
                        "Red Cross"))

@@

```{r plot gp plot}
renderPlotly({
  choice = df()

    persona1 = p_beta1 # Choose the persona

  ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
  gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
  ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
  rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)

    persona2 = p_beta2 # Choose the persona

  ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
  gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
  ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
  rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)

      persona3 = p_beta3 # Choose the persona

  ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
  gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
  ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
  rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)

  data <- c(gp_exp_util1, gp_rate1, 
            gp_exp_util2, gp_rate2,
            gp_exp_util3, gp_rate3)

  df <- as.data.frame(matrix(data, 6, 1))

  df[,2] <- c("Greenpeace")
  df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
  df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
  colnames(df) <- c('Value', 'Organization', "Type", "Persona")

  ggplotly(df %>% filter(Type == "Market Share") %>% 
             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
             geom_bar(position = "dodge", stat = "identity") +
             labs(x="") + 
             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
             theme(legend.position = "none")
    )
})
```

@@

```{r plot ox plot}
renderPlotly({
  choice = df()

    persona1 = p_beta1 # Choose the persona

  ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
  gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
  ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
  rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)

    persona2 = p_beta2 # Choose the persona

  ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
  gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
  ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
  rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)

      persona3 = p_beta3 # Choose the persona

  ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
  gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
  ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
  rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)

  data <- c(ox_exp_util1, ox_rate1, 
            ox_exp_util2, ox_rate2,
            ox_exp_util3, ox_rate3)

  df <- as.data.frame(matrix(data, 6, 1))

  df[,2] <- c("Oxfam")
  df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
  df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
  colnames(df) <- c('Value', 'Organization', "Type", "Persona")

  ggplotly(df %>% filter(Type == "Market Share") %>% 
             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
             geom_bar(position = "dodge", stat = "identity") +
             labs(x="") + 
             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
             theme(legend.position = "none")
    )
})
```

@@

```{r plot rc plot}
renderPlotly({
  choice = df()

    persona1 = p_beta1 # Choose the persona

  ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
  gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
  ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
  rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)

    persona2 = p_beta2 # Choose the persona

  ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
  gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
  ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
  rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)

      persona3 = p_beta3 # Choose the persona

  ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
  gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
  ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
  rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)

  data <- c(rc_exp_util1, rc_rate1, 
            rc_exp_util2, rc_rate2,
            rc_exp_util3, rc_rate3)

  df <- as.data.frame(matrix(data, 6, 1))

  df[,2] <- c("Red Cross")
  df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
  df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
  colnames(df) <- c('Value', 'Organization', "Type", "Persona")

  ggplotly(df %>% filter(Type == "Market Share") %>% 
             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
             geom_bar(position = "dodge", stat = "identity") +
             labs(x="") + 
             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
             theme(legend.position = "none")
    )
})
```

@@

selectInput("p1_news_medium",
         label = "Medium to follow news:",
         choices = c('TV',
                     'Print',
                     "Online",
                     "Social Media",
                     "Radio",
                     "Email newsletters",
                     "News app"))

>>>>

beta_persona_test <- as.data.frame(matrix(rep(0), nrow = 38))

beta_persona_test$levels = c("Persona 1", "Persona 2", "Persona 3", "Chartiy Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "Volunteer Frequence","Personal Activism", "Family Activism", "Religious Membership", "Sport or Recreational Membership", "Art, Music, or Educational Membership","Labor Union Membership", "Political Party Membership", "Environmental Organization Membership", "Professional Association", "Humanitarian or Charity Membership","Consumer Organization Membership", "Other Organization Membership", "Follow National News", "Follow International News", "News Medium","Follow Government or Public Affairs", "Travel to Developing Countries", "Political Preference", "Trust in Political Institutions", "Others Should be Charitable", "Worship Service Attendence", "Religious Importance", "Religion", "Gender", "Marital Status", "Education", "Income", "Race", "Age")

beta_persona_test$p1 <- 1

beta_persona_test$p2 <- 2

beta_persona_test$p3 <- 3

persona1 <- persona_data[,2]

p_beta1 <- as.matrix(public_political_social_charity_demo) %*%

  as.matrix(persona1) %*% beta_persona_test[,3]

@@

renderPlotly({
  org_choice = df()
  per_choice = p()

    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% exp(as.matrix(persona1) %*% t(per_choice[,3]))
#add step to matrix multiply the persona reactive element to the persona data and the public_political beta table.

  ai_exp_util1 <- round(exp(t(org_choice[, 3]) %*% as.matrix(p_beta1)),2)
  gp_exp_util1 <- round(exp(t(org_choice[, 4]) %*% as.matrix(p_beta1)),2)
  ox_exp_util1 <- round(exp(t(org_choice[, 5]) %*% as.matrix(p_beta1)),2)
  rc_exp_util1 <- round(exp(t(org_choice[, 6]) %*% as.matrix(p_beta1)),2)

@@

    # p_beta2 <- as.matrix(public_political_social_charity_demo) %*% (t(per_choice[,4]) %*% as.matrix(persona2))

  ai_exp_util2 <- round(exp(t(org_choice[, 3]) %*% as.matrix(p_beta2)),2)
  gp_exp_util2 <- round(exp(t(org_choice[, 4]) %*% as.matrix(p_beta2)),2)
  ox_exp_util2 <- round(exp(t(org_choice[, 5]) %*% as.matrix(p_beta2)),2)
  rc_exp_util2 <- round(exp(t(org_choice[, 6]) %*% as.matrix(p_beta2)),2)

@@

    # p_beta3 =  as.matrix(public_political_social_charity_demo) %*% (t(per_choice[,5]) %*% as.matrix(persona3))

  ai_exp_util3 <- round(exp(t(org_choice[, 3]) %*% as.matrix(p_beta3)),2)
  gp_exp_util3 <- round(exp(t(org_choice[, 4]) %*% as.matrix(p_beta3)),2)
  ox_exp_util3 <- round(exp(t(org_choice[, 5]) %*% as.matrix(p_beta3)),2)
  rc_exp_util3 <- round(exp(t(org_choice[, 6]) %*% as.matrix(p_beta3)),2)

@@

```{r plot ai plot}
# renderPlotly({
#   choice = df()
#   
#     persona1 = p_beta1 # Choose the persona
#   
#   ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
#   gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
#   ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
#   rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
#   
#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   
#     persona2 = p_beta2 # Choose the persona
#   
#   ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
#   gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
#   ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
#   rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
#   
#   ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
#   gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
#   ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
#   rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
#   
#       persona3 = p_beta3 # Choose the persona
#   
#   ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
#   gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
#   ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
#   rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
#   
#   ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
#   gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
#   ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
#   rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
#   
#   data <- c(ai_exp_util1, ai_rate1, 
#             ai_exp_util2, ai_rate2,
#             ai_exp_util3, ai_rate3)
#   
#   
#   df <- as.data.frame(matrix(data, 6, 1))
#   
#   df[,2] <- c("Amnesty International")
#   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
#   df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
#   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
#   
#   ggplotly(df %>% filter(Type == "Market Share") %>% 
#              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
#              geom_bar(position = "dodge", stat = "identity") +
#              labs(x="") + 
#              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
#              theme(legend.position = "none")
#     )
# })
```

@@

# Some kind of Org Id that could select the organization you are looking at? Not sure how to make it change the label in the graph

@@

```{r plot gp plot}
# renderPlotly({
#   choice = df()
#   
#     persona1 = p_beta1 # Choose the persona
#   
#   ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
#   gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
#   ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
#   rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
#   
#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   
#     persona2 = p_beta2 # Choose the persona
#   
#   ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
#   gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
#   ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
#   rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
#   
#   ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
#   gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
#   ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
#   rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
#   
#       persona3 = p_beta3 # Choose the persona
#   
#   ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
#   gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
#   ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
#   rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
#   
#   ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
#   gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
#   ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
#   rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
#   
#   data <- c(gp_exp_util1, gp_rate1, 
#             gp_exp_util2, gp_rate2,
#             gp_exp_util3, gp_rate3)
#   
#   
#   df <- as.data.frame(matrix(data, 6, 1))
#   
#   df[,2] <- c("Greenpeace")
#   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
#   df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
#   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
#   
#   ggplotly(df %>% filter(Type == "Market Share") %>% 
#              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
#              geom_bar(position = "dodge", stat = "identity") +
#              labs(x="") + 
#              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
#              theme(legend.position = "none")
#     )
# })
```

@@

```{r plot ox plot}
# renderPlotly({
#   choice = df()
#   
#     persona1 = p_beta1 # Choose the persona
#   
#   ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
#   gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
#   ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
#   rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
#   
#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   
#     persona2 = p_beta2 # Choose the persona
#   
#   ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
#   gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
#   ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
#   rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
#   
#   ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
#   gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
#   ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
#   rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
#   
#       persona3 = p_beta3 # Choose the persona
#   
#   ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
#   gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
#   ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
#   rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
#   
#   ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
#   gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
#   ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
#   rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
#   
#   data <- c(ox_exp_util1, ox_rate1, 
#             ox_exp_util2, ox_rate2,
#             ox_exp_util3, ox_rate3)
#   
#   
#   df <- as.data.frame(matrix(data, 6, 1))
#   
#   df[,2] <- c("Oxfam")
#   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
#   df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
#   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
#   
#   ggplotly(df %>% filter(Type == "Market Share") %>% 
#              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
#              geom_bar(position = "dodge", stat = "identity") +
#              labs(x="") + 
#              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
#              theme(legend.position = "none")
#     )
# })
```

@@

```{r plot rc plot}
# renderPlotly({
#   choice = df()
#   
#     persona1 = p_beta1 # Choose the persona
#   
#   ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
#   gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
#   ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
#   rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
#   
#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   
#     persona2 = p_beta2 # Choose the persona
#   
#   ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
#   gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
#   ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
#   rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
#   
#   ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
#   gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
#   ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
#   rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
#   
#       persona3 = p_beta3 # Choose the persona
#   
#   ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
#   gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
#   ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
#   rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
#   
#   ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
#   gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
#   ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
#   rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
#   
#   data <- c(rc_exp_util1, rc_rate1, 
#             rc_exp_util2, rc_rate2,
#             rc_exp_util3, rc_rate3)
#   
#   
#   df <- as.data.frame(matrix(data, 6, 1))
#   
#   df[,2] <- c("Red Cross")
#   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
#   df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
#   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
#   
#   ggplotly(df %>% filter(Type == "Market Share") %>% 
#              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
#              geom_bar(position = "dodge", stat = "identity") +
#              labs(x="") + 
#              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
#              theme(legend.position = "none")
#     )
# })
```

@@

selectInput("p1_news_medium",
         label = "Medium to follow news:",
         choices = c('TV',
                     'Print',
                     "Online",
                     "Social Media",
                     "Radio",
                     "Email newsletters",
                     "News app"),
         multiple = TRUE)
